\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{overpic}
\usepackage{xcolor}
\usepackage{hyperref}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\newcommand\todo[1]{\textcolor{red}{TODO #1}}

\begin{document}

\title{Virtual Neurorobotics in the Human Brain Project}
\author{Max Becker, Olivier Boder and Qianlin Wu\\FZI Forschungszentrum Informatik\\Karlsruhe, Germany}

\maketitle
\thispagestyle{plain}
\pagestyle{plain}

\begin{abstract}
In this paper the challenge for the neurorobotics praktikum is presented and some solutions are discussed.
The challenge and some theoretic background are explained in the beginning followed by the attempted solutions.
The first solution is a hard-coded throw and the second one a learning approach using evolutionary algorithms and spiking neural networks.
\end{abstract}


\begin{IEEEkeywords}
Spiking Neural Networks, Evolutionary Algorithms, Neurorobotics Platform, Human Brain Project
\end{IEEEkeywords}


\input{sections/introduction}
\input{sections/evolutionaryalgorithm}
\input{sections/spiking}
\input{sections/hardcodedapproach}
\input{sections/learnedapproaches}
\input{sections/problems}
\input{sections/results}
\input{sections/conclusion}


\begin{thebibliography}{00}
\bibitem{b1} G. Eason, B. Noble, and I. N. Sneddon, ``On certain integrals of Lipschitz-Hankel type involving products of Bessel functions,'' Phil. Trans. Roy. Soc. London, vol. A247, pp. 529--551, April 1955.
\end{thebibliography}


\end{document}
